\datedlocatedsubsection{Sep 2023 -- Sep 2024 }
{\textbf{University of Manchester, UK}}
{\textbf{M.Sc. Advanced Computer Science -- Cyber Security focus}}
{
    \textbf{Currently in progress}
    \\\textbf{Dissertation:} Intrusion Detection in a Foreign Domain.
    \\\textbf{Key Modules:} Automated Reasoning and Verification, Software Security, Modelling and Querying Data on the Web, Cyber Security and Cryptography.

}

\datedlocatedsubsection{Sep 2018 -- Jun 2022 }
{\textbf{Aston University, Birmingham, UK}}
{\textbf{B.Sc. Business Computing and Information Technology}}
{
    \textbf{Graduated with First Class Honours }
    \textbf{Dissertation:} Research and Development on the Supply Chain and Logistics of the Energy and Bioproducts Research Institute (EBRI) at Aston University
    \begin{itemize}
        \item \textbf{Key Modules:} Database Applications [SQL, MSAccess] (79.6\%), Applications Development [C\#] (82\%), Systems Analysis (78\%), Information Security (81\%), Project Delivery (76\%), BCIT Research project[Supply Chain]  (78\%).
        \item Served as Student Course Representative for Business Computing and IT, conducting research and
        development for course enhancements. Proposed module-specific improvements that significantly
        influenced the degree experience.
        \item Gained leadership experience as Vice President of the Aston Bright Futures Society, part of the largest network of university societies with a focus on professional development in the UK.
        \item Played a pivotal role in organizing events, workshops, and networking opportunities for members, significantly contributing to their professional growth and the society's reputation.
        \item Earned the Societies Federation Silver Award for my contribution in the Bright Futures Society.
    \end{itemize}
}

\datedlocatedsubsection{Sep 2017 -- Jun 2018 }
{Network Foundation School, Athens, Greece}
{\textbf{Foundation Year} Focus on Business and IT}
{
    \textbf{Final grade: 80\% (AAB).}
    \begin{itemize}
        \item \textbf{Key Modules:} Computing 83\%, Statistics 85\%, Business and Economics 85\%, Project Development 80\% [research and large audience group presentation], Programming [C++, Python] 80\% .
        \item Acquired valuable skills in delivering presentations to large audiences, mastering the principles of effective teamwork, and honing research and time management abilities through extensive academic projects and assignments.
    \end{itemize}
}

\datedlocatedsubsection{Sep 2015 -- Jun 2018 }
{}
{2nd Lyceum, Argyroupolis, Athens, Greece}
{\textbf{General Lyceum Apolyterium, GPA of graduation ‘Excellent’ 18.9/20.0.}}
