\begin{itemize}
      \item Ethical Hacking
            \begin{itemize}
                  \item Engaged in ethical hacking studies, including CaptureTheFlag and HackTheBox exercises. Actively
                        seeking out events to enhance technical skills in practice, with ongoing courses in Linux and Red
                        Teaming at HtB Academy.
                  \item Contributed to team-based coding challenges at the Great Uni Hackathon 2023 and currently
                        participating in StudentHack 2024 at the University of Manchester, enriching my experience in
                        teamwork and coding.
            \end{itemize}
      \item A dedicated swimmer since childhood, actively competing in university competitions, including
            BUCS racing. Represented Aston University during my undergraduate years and continued at the University
            of Manchester during my master's program. It is a sport that taught me about consistency and calmness
            through pressure, endurance through exhaustion and team building through training.

\end{itemize}

\vspace{10pt}

\textbf{Digital Skills:}
Microsoft Office | Python | Git | SQL | C++ | C\# | JAVA | Linux | Node.Js | React.Js | HTML/CSS/
JavaScript

\vspace{10pt}

\textbf{Languages :}
\begin{itemize}
      \item Native: Greek.
      \item Fluent: English (IELTS Band score [7] in 2018), Studied for 5 years in England 2018-2022 and 2023-2024.
      \item Beginner/B1: German.
\end{itemize}

\textbf{EU Driving Licence (GREEK):} since August 2018.