\documentclass[]{prometheus_cv}
\usepackage[a4paper, total={5.3in, 10in}, top=2cm]{geometry}

\usepackage{xcolor}
\definecolor{highlight}{HTML}{283559}
\definecolor{highlight2}{HTML}{1A2640}
\definecolor{link}{HTML}{5C6273}

\usepackage{lipsum}
\usepackage{siunitx}
\usepackage{fontawesome5}
\usepackage[super]{nth}
\usepackage{multicol}
\usepackage[
    colorlinks = true,
    linkcolor = highlight,
    urlcolor = highlight,
    citecolor= highlight
]{hyperref}
\usepackage{fontspec}
\usepackage{fancyhdr}

\setmainfont[
    BoldFont=Cormorant Garamond Bold,
    ItalicFont=Cormorant Garamond Italic,
    BoldItalicFont=Cormorant Garamond Bold Italic
]{Cormorant Garamond Regular}
\newfontfamily\GaramondLight{Cormorant Garamond Light}
\newcommand\textlf[1]{{\GaramondLight#1}}
\newcommand{\highlight}[1]{\textcolor{highlight}{\textbf{#1}}}
\newcommand{\ec}{\textsuperscript{\textdagger}}

\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\begin{document}
\thispagestyle{empty}
\pagestyle{fancy}

\centering

\begin{huge}
    Nikolaos Karaolidis
\end{huge}

\begin{footnotesize}
    \begin{tiny}\faMobile*\end{tiny}~\href{tel:+447947145598}{+44 7947145598}
    \quad
    %\begin{tiny}\faMobile*\end{tiny}~\href{tel:+306979252518}{+30 6979252518}
    %\quad
    \begin{tiny}\faHome\end{tiny}~\href{www.karaolidis.com}{karaolidis.com}
    \quad
    \begin{tiny}\faEnvelope\end{tiny}~\href{mailto:nick@karaolidis.com}{nick@karaolidis.com}
    \quad
    \begin{tiny}\faLinkedinIn\end{tiny}~\href{https://www.linkedin.com/in/nikolaos-karaolidis/}{nikolaos-karaolidis}
    \quad
    \begin{tiny}\faGitlab\end{tiny}~\href{https://git.karaolidis.com/karaolidis}{karaolidis}
    \quad
    \begin{tiny}\faGithub\end{tiny}~\href{https://github.com/karaolidis}{karaolidis}
    %\quad
    %\begin{tiny}\faGitlab\end{tiny}~\href{https://gitlab.cs.man.ac.uk/k11980nk}{k11980}
\end{footnotesize}

\section{Education}

\datedsubsection{Sep 2020 -- Jul 2024}
{University of Manchester, UK}
{\textbf{M.Eng.} in Computer Science}
{\textbf{First-Class} Honours}

\datedsubsection{Sep 2014 -- Jun 2020}
{Varvakeio Public Model High School, Greece}
{High School Diploma}
{\textbf{\nth{12} Grade Average:} 96\%}

\section{Work Experience}

\datedsubsection{Jun 2023 - Sep 2023}
{}
{WebHotelier | primalRES -- Athens, Greece -- Software Engineering Intern}
{
    With 9000+ customers in 38 countries, WebHotelier | primalRES stands as the leading travel tech group in Greece and one of the giants in Europe.
    \begin{itemize}
        \item Spearheaded a complete overhaul of the company's \textbf{Grafana} dashboards, slashing the time-to-load by approximately 80\% while also increasing the number of metrics shown.
        \item Collaborated directly with the CTO to secure a year-long contract with \textbf{ClickHouse Cloud} and \textbf{AWS}.
        \item Migrated the entire metrics stack from \textbf{InfluxDB} to \textbf{ClickHouse}. This shift amped up performance by over 50\% without inflating operational costs.
        \item Engineered an open-source \textbf{Telegraf} ClickHouse plugin optimized for Terabyte-scale data outputs, outperforming the in-built plugin in terms of efficiency.
        \item Deployed Telegraf across 12 \textbf{Amazon EC2} instances, a move which unveiled and subsequently led to rectifying several performance bottlenecks.
        \item Modernized the logging approach by transitioning to \textbf{ClickHouse}, thereby ending the thread-related challenges of the erstwhile file-based system.
        \item Teamed up with fellow developers to incorporate \textbf{DataDog} APM into \textbf{Java} applications, shedding light on intricate application operations and pinpointing areas of enhancement.
    \end{itemize}
}

\datedsubsection{Jun 2022 - Aug 2022}
{}
{Softwire -- Manchester, UK -- Software Engineering Intern}
{
    Working with some of the UK's leading brands, Softwire designs tailored software and delivers innovative digital engineering expertise.
    \begin{itemize}
        \item Co-developed a web app using \textbf{React Native}, \textbf{Typescript}, \textbf{AWS Lambda}, and \textbf{AWS DynamoDB} in a 6-person team.
        \item Participated in daily stand-ups, retrospectives, sprint planning, and review meetings.
        \item Authored clean and maintainable code which was tested using unit, integration, and end-to-end testing.
    \end{itemize}
}

\datedsubsection{Jul 2019}
{}
{InterSearch Worldwide -- Dubai, UAE -- Intern}
{
    Ranked among the 30 largest executive search firms in the world, InterSearch Worldwide has 90 offices in 50 different countries.
    \begin{itemize}
        \item Developed a \textbf{Python CLI Tool} to automate Candidate CV and Financial Documentation Entry, extracting information from .pdf, .doc, and .docx CVs to the \textbf{FileFinder} database.
        \item Incorporated \textbf{XML parsing} techniques for data extraction from Microsoft Word documents.
        \item Employed \textbf{Optical Character Recognition with OpenCV} to interpret non-editable PDFs.
        \item Applied \textbf{Natural Language Processing using NLTK} to categorize text tokens such as names, addresses, and skills.
        \item Navigated database interactions using \textbf{PyAutoGUI}, a workaround due to limited direct database access.
        \item Refined the E-mail spam filter to improve internal communications.
    \end{itemize}
}

\section{Projects}

\datedsubsectionnarrow{Ongoing}
{}
{Personal Homelab}
{
    Adapted an old PC into a \textbf{Linux Server} for 40+ applications. Mainly used as a way to learn the latest technologies, practice new skills, and as a host for personal projects.
    \begin{itemize}
        \item \textbf{Arch Linux} as the base OS with \textbf{MergerFS} and \textbf{SnapRAID} as a storage and backup solution.
        \item \textbf{Docker}, \textbf{Docker Compose}, and \textbf{Portainer} as a container engine and management system.
        \item \textbf{Cloudflare Argo Tunnel}, \textbf{Nginx}, and \textbf{Let’s Encrypt} for hosting, proxying, and SSL certificate automation.
        \item \textbf{Grafana}, \textbf{InfluxDB}, and \textbf{Telegraf} for constant system monitoring, stats visualization, and email alerts.
        \item \textbf{DevOps Stack} including a self-hosted \textbf{GitLab} instance and \textbf{VSCode server}.
        \item Public and private \textbf{Wireguard} instances and a \textbf{Tor} relay for remote management and privacy.
        \item Full-stack \textbf{media management server} including indexing, file downloading, metadata editing, and a personal streaming service.
        \item Much more, including a \textbf{blog}, a \textbf{private cloud} service for family/friends, and a URL shortener.
    \end{itemize}
}

\datedsubsectionnarrow{Sep 2022 - Apr 2023}
{}
{Trailblazer}
{
    Third Year University Project. Collaborated with a research group from Lancaster University to develop an \textbf{OS performance evaluation platform}. Built using Go and Python. A paper was later submitted to the \textbf{International Conference on Architectural Support for Programming Languages and Operating Systems (ASPLOS) 2024}.
    \begin{itemize}
        \item Designed experiments to benchmark performance of network-based applications such as \textbf{Apache} and \textbf{Caddy}.
        \item Implemented multiple-architecture support using the \textbf{QEMU} virtual machine emulator, focusing on \textbf{x86-64} and \textbf{RISC-V}.
        \item Conducted testing and analysis to derive a memory-optimized \textbf{Linux} kernel configuration.
        \item Performed maintenance and bug fixes on the \textbf{Go} codebase and reduced experiment runtime using \textbf{RAM-based filesystems}.
    \end{itemize}
}

\datedsubsectionnarrow{Sep 2020 - Jun 2021}
{}
{EazyShop}
{
    First Year University Project. Worked in a 6-person team to implement a \textbf{full-stack shopping list application}. Built using Python, Flask, HTML, Bootstrap, and MySQL.
    \begin{itemize}
        \item Configured and hosted a shared \textbf{MySQL} database using \textbf{Docker} for portability.
        \item Implemented \textbf{web scrapers} using \textbf{Python} for the 6 largest UK grocery store chains. Used to extract, parse, and import stock, pricing, and descriptions from all available products.
        \item Integrated the \textbf{MySQL} back-end with the \textbf{Flask} front-end and deployed the app using \textbf{Docker Compose}.
    \end{itemize}
}

\section{Languages}
\begin{itemize}
    \item Native: Greek, Serbocroatian
    \item Fluent/C2: English
    \item Beginner/B1: German
\end{itemize}

\end{document}
