\datedlocatedsubsection{Sep 2022 - Sep 2023}
{\textbf{Hellenic Airforce, Athens, Greece}}
{SYSTEMS ADMINISTRATOR ASSISTANT}
{
    Served in the IT department of the Hellenic Air Force as part of my military service in Greece, with
    responsibilities including:
    \begin{itemize}
        \item Main domain: Sysadmin (Systems Administrator)
        \item Installed and configured servers, hardware, and software.
        \item Managed system security, including implementing firewalls and managing permissions.
        \item Created and managed user accounts and access controls.
        \item Performed regular backups and recovery operations.
        \item Applied system updates, patches, and routine maintenance.
        \item Collaborating in a team to develop web applications for internal systems of the Hellenic Air Force, mainly utilizing
              the React framework, enhancing digital accessibility and operational efficiency.
    \end{itemize}
}

\datedlocatedsubsection{Sep 2020 - May 2021}
{Skywalk Transport and Logistics, Athens, Greece }
{Operations and IT Intern}
{

    Placement working experience as part of my studies, in a Supply Chain Company dealing with B2B deliveries.
    \begin{itemize}
        \item Audited two ERP systems for enhanced management of parcels, orders, and vehicles.
        \item Supervised a collaboration project with DB Schenker, overseeing communications, parcel order management, driver routing systems, and auditing processes.
        \item Maintained and developed the company's website using React 16, improving user interface and functionality.
        \item Provided technical support within the office, addressing and resolving a wide range of IT issues.
        \item Developed a calculator program with a GUI in C\#, which halved the time spent on report creation and facilitated easier data visualization.
        \item Implemented an Access database as a quick and effective solution to meet the company's data management and storage needs, significantly improving organizational efficiency.

    \end{itemize}
}

\datedlocatedsubsection{Aug 2017 - Aug 2018}
{“Virus” Men’s wear retail store, Megara, Greece}
{Sales Assistant}
{
    Part-time position at a small retail company:
    \begin{itemize}
        \item Developed and maintained the store’s website using React and MongoDB.
        \item Managed communications with suppliers for merchandise orders.
        \item Oversaw the visual merchandising and inventory management of the storefront, enhancing product presentation and optimizing stock levels.
    \end{itemize}
}
